A thesis draft

### 2018-12-02 res/sections/07-Introduction.tex
Add prof corrections (#15)
- Fix #14 - Add prof corrections
- Fix #13 - Swap table columns, add saved configurations

This new possibility of provisioning a network with specialized, heterogeneous
classes of services, combined with emerging virtualization technologies like
cloud computing, hypervisor-virtualized machine or container-based solutions,
enables the deployment of Virtualized Network Functions (VNFs) within seconds
running on generic purpose or custom hardware. Even though the use
virtualization is sometimes paid in terms of computational overhead, the
technology has demostrated its maturity and the possibilities of automation it
offers are unprecedented~\cite{nguyen2017sdn}. On top of that, a specialized
software entity acts as a MANager and Orchestrator (MANO) for these VNFs,
managing their lifecycle. While most of the current proposals are based on a
hypervisor solution, in this thesis we set the objective of providing a
proof-of-concept implementation of an Infrastructure Management and
Orchestration plane based on the new container-based technology, called Docker,
on a recent orchestrator framework: Kubernetes. Moreover, building on recent
published results of the 3GPP Release 15, we outline a software architecture
capable of end-to-end service orchestration exploiting container-technology.

@@

This thesis is organized as follows:
\begin{itemize}
 \item Chapter~\ref{chap:background} provides some background information about
   5G and the technologies used to build an ETSI compliant architecture;
 \item Chapter~\ref{chap:rel_wk} discusses some prior work of relevance in the
   context;
 \item Chapter~\ref{chap:prjan} provides a detailed analysis of the domain,
   fixing some design requirments, stating the overall project roadmap.
 \item Chapter~\ref{chap:archimpl} provides an in-depth view of the high-level
   architectural implementation;
 \item Chapter~\ref{chap:vnf_ns_impl} gives a brief explanation of the SFC
   implementation;
 \item Chapter~\ref{chap:test} discusses the experimental setting along with
   some obtained preliminary results
 \item Chapter~\ref{chap:fw} illustrates possible future works;
 \item Chapter~\ref{chap:conclusions} wraps up the overall project experience.
\end{itemize}

>>>>

This new possibility of provisioning a network with specialized, heterogeneous
classes of services, combined with emerging virtualization technologies like
cloud computing, hypervisor-virtualized machine or container-based solutions,
enables the deployment of Virtualized Network Functions (VNFs) within seconds
running on generic purpose or custom hardware. Even though the use
virtualization is sometimes paid in terms of computational overhead, the
technology has demonstrated its maturity and the possibilities of automation it
offers are unprecedented~\cite{nguyen2017sdn}. On top of that, a specialized
software entity acts as a MANager and Orchestrator (MANO) for these VNFs,
managing their lifecycle. While most of the current proposals are based on a
hypervisor solution, in this thesis we set the objective of providing a
proof-of-concept implementation of an Infrastructure Management and
Orchestration plane based on the new container-based technology, called Docker,
on a recent orchestrator framework: Kubernetes. Moreover, building on recent
published results of the 3GPP Release 15, we outline a software architecture
capable of end-to-end service orchestration exploiting container-technology.

@@

This thesis is organized as follows:
\begin{itemize}
 \item Chapter~\ref{chap:background} provides some background information about
   5G and the technologies used to build an ETSI compliant architecture;
 \item Chapter~\ref{chap:rel_wk} discusses some prior work of relevance in the
   context;
 \item Chapter~\ref{chap:prjan} provides a detailed analysis of the domain,
   fixing some design requirements, stating the overall project roadmap.
 \item Chapter~\ref{chap:archimpl} provides an in-depth view of the high-level
   architectural implementation;
 \item Chapter~\ref{chap:vnf_ns_impl} gives a brief explanation of the SFC
   implementation;
 \item Chapter~\ref{chap:test} discusses the experimental setting along with
   some obtained preliminary results
 \item Chapter~\ref{chap:fw} illustrates possible future works;
 \item Chapter~\ref{chap:conclusions} wraps up the overall project experience.
\end{itemize}

### 2018-12-02 res/sections/10-ProjectAnalysis.tex
Add prof corrections (#15)
- Fix #14 - Add prof corrections
- Fix #13 - Swap table columns, add saved configurations

As discussed through Chapter ~\ref{chap:intro}, the implementation of an
ETSI-compliant MANO architecture, contemplating service chain proovisioning
capabilities as mandated by RFC 7665, requires the integration of multiple
tools. The tools were chosen after their analysis, where pro and cons have been
studied and compared to the necessity of this thesis. Since the project has been
developed within the cloud environment provided by the Department of
Mathematics, University of Padua, we initially relied on Openstack (which a
product analysis can be found later in~\ref{chap:prjan:sec:openstack}) as the
default infrastructure manager choice.

>>>>

As discussed through Chapter ~\ref{chap:intro}, the implementation of an
ETSI-compliant MANO architecture, contemplating service chain provisioning
capabilities as mandated by RFC 7665, requires the integration of multiple
tools. The tools were chosen after their analysis, where pro and cons have been
studied and compared to the necessity of this thesis. Since the project has been
developed within the cloud environment provided by the Department of
Mathematics, University of Padua, we initially relied on Openstack (which a
product analysis can be found later in~\ref{chap:prjan:sec:openstack}) as the
default infrastructure manager choice.
